X\texorpdfstring{\textsuperscript{2}}.-Toon: An Extended X-Toon Shader

### 2013-04-15 paper/paper.tex
Small editing
Final editing

\documentclass[annual]{acmsiggraph}
\usepackage{wrapfig}
\usepackage{hyperref}
\title{X\texorpdfstring{\textsuperscript{2}}-Toon: An Extended X-Toon Shader}

@@

The X-toon shader ~\cite{BTM06a} extended classic cel shading from 1D shading texture to 2D texture. The second dimension ``corresponds to the desired `tone detail' ''. In this paper, we look to extend the initial offering of the X-Toon shader and develop new methods for calculating shading values and tone detail. Additionally, we extend the original shader to allow the use of model textures and transparency within a tone detail texture. This gives artists the tools to create new effects that were not possible with original X-Toon shader.

@@

\subsection{Animated tone detail texture}
We also discussed the possibility of using an animated tone detail texture in lieu of a static image. This could create many new effects such as hologram noise and colour shifting without the need to change tone detail or shading values. Futures works should investigate the use of an animated tone detail texture and devise new effects that can be generated with this method.

>>>>

\documentclass[annual]{acmsiggraph}
\usepackage{wrapfig}
\usepackage{hyperref}
\title{X\texorpdfstring{\textsuperscript{2}}.-Toon: An Extended X-Toon Shader}

@@

The X-toon shader ~\cite{BTM06a} extended classic cel shading from 1D shading textures to 2D textures. The second dimension ``corresponds to the desired `tone detail' ''. In this paper, we look to extend the initial offering of the X-Toon shader and develop new methods for calculating shading values and tone detail. Additionally, we extend the original shader to allow the use of model textures and transparency within a tone detail texture. This gives artists the tools to create new effects that were not possible with original X-Toon shader.

@@

\subsection{Animated tone detail texture}
We also discussed the possibility of using an animated tone detail texture in lieu of a static image. This could create many new effects such as hologram noise and colour shifting without the need to change tone detail or shading values. Future works should investigate the use of an animated tone detail texture and devise new effects that can be generated with this method.
